---
# title: "Supplementary Materials"
author: "Elena Chechik"
org: "Center for Institutional Analysis of Science & Education European University at St. Petersburg"
---

### Supplementary Materials

# Gender, Parenthood, and Academic Performance: Work-life and Work-work Balance in Russian Academia

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,  warning = FALSE, message =  FALSE)
```

```{r packages}
library(tidyverse)
library(coefplot) 
library(table1)
library(ggpubr) 
library(patchwork)
library(ggpmisc) 
library(DT)
library(likert)
library(kableExtra)
library(stargazer)
library(scales)
library(ggrepel)
```

```{r functions}
pvalue <- function(x, ...) {
    # Construct vectors of data y, and groups (strata) g
    y <- unlist(x)
    g <- factor(rep(1:length(x), times=sapply(x, length)))
    if (is.numeric(y)) {
        # For numeric variables, perform a standard 2-sample t-test
        p <- t.test(y ~ g)$p.value
    } else {
        # For categorical variables, perform a chi-squared test of independence
        p <- chisq.test(table(y, g),correct = TRUE, simulate.p.value = TRUE, B = 10000)$p.value
    }
    # Format the p-value, using an HTML entity for the less-than sign.
    # The initial empty string places the output on the line below the variable label.
    c("", sub("<", "&lt;", format.pval(p, digits=3, eps=0.001)))
}
```

```{r data}
set <- read_csv("~/Desktop/EGOS2023/data/set.csv")

set_uni <- set %>% 
  filter(wave == 'wave_1_2'| wave == 'wave_2_5' | wave ==  'wave_2_6') %>% 
  filter(age_int >= 21 & age_int <= 80) %>% 
  filter(type_doj != "Другое") %>% 
  filter(org_type == "Ведущий вуз" | org_type == "Вуз") %>% 
  rename(gender = sex)

```

```{r pallets}
#col_gender <- c("#ffe043","#b3b3b3")
col_gender2 <- c("#f5d64d","#b3b3b3")
col_gender3 <- c("#ffd91a","#b3b3b3")
col_gap <- c("#91C45A", "#C19AD6")

#show_col(col_gender)
```

### Table S1: Sample Selection Criteria and Procedure

<center>
![](pics/Table_S1_sample_selection.svg){width=45%}
</center>


### Table S2: List of Leading Universities

```{r}
#| fig-align: 'center'

Tab_1 <- read_delim("data/top_uni_list.csv", 
    delim = ";", escape_double = FALSE, col_names = FALSE, 
    trim_ws = TRUE)
Tab_1$X3[is.na(Tab_1$X3)] <- " "

kable(Tab_1,
      # align = c("l","c"),
      col.names = c("#","University", "Comment"),
      escape = FALSE) %>% 
  kable_styling(full_width = F, position = "center", font_size = 12) %>% 
  #kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "4em") 
  
```

### Table S3: Mean Age at First Child Appearance among Women and Men in the Sample

```{r}
#| fig-align: 'center'

Tab_1 <- table1(~ first_ch_age 
                #+ kan_age
                | gender, data = set_uni,
                overall = FALSE,
                extra.col=list(`P-value`=pvalue))
Tab_1 <- as.data.frame(Tab_1)[-1, ]
Tab_1 <- Tab_1[-1, ] 
#Tab_1[1, 1] <- "Age of first child"
#Tab_1[5, 1] <- "Age of Ph.D. defense"
rownames(Tab_1) <- NULL

kable(Tab_1,
      align = c("l","c", "c", "r"),
      col.names = c(" ","Women<br/> (N=1340)", "Men<br/> (N=736)", "p-value"),
      escape = FALSE) %>%
  kable_styling(full_width = F, position = "center", font_size = 12) 
```

### Figure S1: Dynamics of Age at First Birth for Women in the General Population in Russia

```{r, out.width=550}
#| fig-align: 'center'

ros <- read_delim("data/rosstat.csv", 
                  delim = ";", escape_double = FALSE, trim_ws = TRUE)
ros <- ros %>% 
  pivot_longer(c(`19 и <`:`не указан \nnot stated`), names_to = "age", values_to = "count")

ros1 <- ros %>% mutate(sh = 100 * count / `\nTotal`,
               sh = round(sh, digits = 2)) %>% 
  filter(`\nYears` >= 2000) %>% 
  mutate(age = if_else(age == "50 и >", "50 и >", age)) %>% 
  filter(age != "не указан \nnot stated") 

ggplot() +
  geom_line(data = ros1, aes(`\nYears`, sh, group = age, color = age )) +
  geom_point(data = ros1, aes(`\nYears`, sh, group = age, color = age )) +
  geom_text_repel(data = ros1 %>% filter(`\nYears` == last(`\nYears`)), 
                  aes(label = age, 
                      x = `\nYears` + 1,
                      y = sh,
                      color = age), 
                  nudge_x = 0, direction = "y", 
                  hjust = "center", box.padding = -0.01) +
  guides(color = FALSE) +
  scale_x_continuous(breaks = scales::pretty_breaks(10)) +
  scale_color_brewer(palette = "Dark2", direction = -1) +
  labs(x = "" , y = "Share of Age Group (%)",
       caption = "Data: Russian Statistical Agency") +
  theme_test() + 
  theme(axis.title.x = element_blank(),
        panel.grid.major.y = element_line(size = 0.1, color = "grey70", linetype = "solid"),
        legend.position = "right",
        legend.title = element_blank(),
        plot.caption = element_text(face = "italic")) 
```


### Table S4: Comparison of Publication Productivity between Men and Women by Parenthood Status

```{r}
#| fig-align: 'center'
df_0_ch <- set_uni %>% filter(v_299_2 == "0")  
df_1_ch <- set_uni %>% filter(v_299_2 == "1") 
df_2_ch <- set_uni %>% filter(v_299_2  == "2") 
# df_3_and_more_ch <- df %>% filter(v_299_2 == "3 и >")


Tab_1 <- table1(~  n_rinc +
         n_rinc_core +
         age_int
       | gender , data = df_0_ch, 
       overall = FALSE,
       extra.col=list(`P-value`=pvalue))

Tab_1 <- as.data.frame(Tab_1)[-1, ]
#Tab_1 <- Tab_1[-1, ] 
Tab_1[1, 1] <- "Total publications in RISC"
Tab_1[4, 1] <- "RISC Core publications"
Tab_1[7, 1] <- "Age of respondent"
rownames(Tab_1) <- NULL

Tab_2 <- table1(~  n_rinc +
          n_rinc_core +age_int
       | gender , data = df_1_ch, 
       overall = FALSE,
       extra.col=list(`P-value`=pvalue))

Tab_2 <- as.data.frame(Tab_2)[-1, ]
#Tab_1 <- Tab_1[-1, ] 
Tab_2[1, 1] <- "Total publications in RISC"
Tab_2[4, 1] <- "RISC Core publications"
Tab_2[7, 1] <- "Age of respondent"
rownames(Tab_2) <- NULL
Tab_2 <- Tab_2[, -1] 

Tab_3 <- table1(~  n_rinc +
         n_rinc_core + age_int
       | gender , data = df_2_ch, 
       overall = FALSE,
       extra.col=list(`P-value`=pvalue))

Tab_3 <- as.data.frame(Tab_3)[-1, ]
Tab_3[1, 1] <- "Total publications in RISC"
Tab_3[4, 1] <- "RISC Core publications"
Tab_3[7, 1] <- "Age of respondent"
rownames(Tab_3) <- NULL
Tab_3 <- Tab_3[, -1] 

Tab <- cbind(Tab_1, Tab_2, Tab_3)


kable(Tab,
      align = c("l","c", "c", "r",
                "c", "c", "r",
                "c", "c", "r"),
      col.names = c(" ","Women<br/> (N=303)", "Men<br/> (N=165)", "p-value",
                    "Women<br/> (N=543)", "Men<br/> (N=204)", "p-value",
                    "Women<br/> (N=412)", "Men<br/> (N=254)", "p-value"),
      escape = FALSE) %>%
  kable_styling(full_width = F, position = "center", font_size = 10) %>% 
  add_header_above(c(" ", "No Children" = 3, "One Child" = 3, "Two Children" = 3))
  
```
### Table S5: Regression Analysis of Publication Productivity

```{r, results = "asis"}
#| fig-align: 'center'
positions <- read_delim("~/Desktop/EGOS2023/data/positions.csv", delim = ";",
                        escape_double = FALSE, trim_ws = TRUE)

reg <- set_uni %>% group_by(short_doj_new) %>%
  mutate(short_check = case_when(n() > 40 ~ short_doj_new,
                                 TRUE ~ "другое")) %>%
  left_join(positions, by = c("short_check" = "ru")) %>% 
  filter(!is.na(v_299_2)) %>% 
  select(v_299_2, gender, n_rinc_core, n_rinc, age_int, en, org_type) %>% 
  mutate(child = case_when(v_299_2 == "0" ~ "No Children",
                             TRUE ~ "One or more")) %>% 
  mutate(have_child = case_when(v_299_2 != "0" ~ 1,
                                TRUE ~ 0)) %>% 
  mutate(no_child = case_when(v_299_2 == "0" ~ 1,
                                TRUE ~ 0)) %>% 
  mutate(men = case_when(gender == "Male" ~ 1,
                                TRUE ~ 0)) %>% 
  mutate(women = case_when(gender == "Female" ~ 1,
                                TRUE ~ 0))

fit1 <- lm(n_rinc_core ~ gender + age_int + have_child + #child:sex +
             relevel(as.factor(en), ref = "Head of Department") + org_type, data = reg) 
fit1a <- lm(n_rinc_core ~ gender + age_int + have_child + women:have_child +
             relevel(as.factor(en), ref = "Head of Department") + org_type, data = reg) 
# fit1b <- lm(n_rinc_core ~ gender + age_int + child + men:have_child +
#              relevel(as.factor(en), ref = "Head of Department") + org_type, data = reg) 
# fit1c <- lm(n_rinc_core ~ gender + age_int + child + women:have_child +
#              relevel(as.factor(en), ref = "Head of Department") + org_type, data = reg) 

fit2 <- lm(n_rinc ~ gender + age_int + have_child + #child:sex +
             relevel(as.factor(en), ref = "Head of Department") + org_type, data = reg) 
fit2a <- lm(n_rinc ~ gender + age_int + have_child + women:have_child +
             relevel(as.factor(en), ref = "Head of Department") + org_type, data = reg) 

reg1 <- stargazer(fit1, fit1a,fit2,fit2a, header=FALSE, #type = 'html',
               #type="html", #dep.var.labels=c("Core", "All Pubs"),
          #title="Table 2: Regression Results", 
          digits = 1, out = "table1.html",
          dep.var.labels = c("RISC Core", "Total RISC"),
          covariate.labels = c("Male",
                               "Age",
                               "Have child",
                               "Assistant Lect vs Head of Dep",
                               "Associate Prof vs Head of Dep",
                               "Full Professor vs Head of Dep",
                               "Lecturer vs Head of Dep",
                               "Other positions vs Head of Dep",
                               "PhD student vs Head of Dep",
                               "Uni vs Top Uni"))


htmltools::includeHTML("table1.html")

```

